Hochschild cohomology of torus-equivariant D-modules

### 2015-06-23 paper.tex
Adapt labeling.

A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
We will review the general setup and basic properties of D-modules on (QCA) stacks in Chapter~\ref{ch:d-mod:pre}.
The upshot is that we have an isomorphism of dg algebras
\begin{equation}
    \label{eq:intro:d-mod:d-mod-hcoh}
    \HCoh(\catDMod{\stack X}) \cong \Hom_{\catDMod{X×X}}(Δ_*ω_{\stack X}, Δ_*ω_{\stack X}),
\end{equation}
where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Lemma show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de Rham cohomology of $\stack X$.
However, if $\stack X$ is not an algebraic space (and hence $Δ$ is not proper) then the situation becomes more complicated.

By Verdier duality and adjunction we can always rewrite \eqref{eq:intro:d-mod:d-mod-hcoh} as
\[
    \HCoh(\catDMod{\stack X}) \cong
    \opalg{\Hom_{\catDMod{X}}(k_{\stack X}, Δ^!Δ_!k_{\stack X})} =
    \opalg{\ΓdR(\stack X, Δ^!Δ_!k_{\stack X})}.
\]
It is now tempting to look at the Cartesian square
\[
    \begin{tikzcd}
        \ls \stack X \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
where
\[
    \ls \stack X = \stack X ×\limits_{\stack X × \stack X} \stack X
\]
is the (derived) loop space of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
Naively we could expect the existence of an isomorphism
\begin{equation}
    \label{eq:intro:d-mod:naive}
    \ΓdR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
    \ΓdR(\stack X, p_{2,!}p₁^! k_{\stack X}).
\end{equation}
Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\as1$ is an easy counter-example).

In Chapter~\ref{ch:d-mod:strategy} we will investigate how to quantify the cone of the morphism
\[
    p_{2,!}p₁^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
\]
and thus the failure of the naive isomorphism \eqref{eq:intro:d-mod:naive} to hold.
As an application, we will prove the following theorem, giving a class of stacks where \eqref{eq:intro:d-mod:naive} is indeed an isomorphism.

\begin{Thm}\label{thm:d-mod:main}
    Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
    Then there is a canonical isomorphism of algebras
    \[
        \HCoh\bigl(\catDMod{X/G}\bigr)
        \cong
        \opalg{\ΓdR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)},
    \]
    where the algebra structure on $\ΓdR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
\end{Thm}

\section{Prerequisites}%
\label{ch:d-mod:pre}

We fix an algebraically closed base field $k$ of characteristic $0$.
All stacks in this thesis are assumed to be algebraic QCA stacks over $k$.
As we will summarize in Section~\ref{sec:d-mod:pre:d-mods}, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
In particular for any stack $\stack X$ we have:
\begin{itemize}
    \item The diagonal morphism $Δ\colon \stack X → \stack X × \stack X$ is schematic.
    \item There exists a scheme $Z$ with a smooth and surjective map $Z → \stack X$.
    \item $\stack X$ is quasi-compact.
    \item The automorphism groups of the geometric points of $\stack X$ are affine.
    \item The loop space (or inertia stack) $\ls \stack X = \stack X ×_{\stack X × \stack X} \stack X$ is of finite presentation over $\stack X$.
\end{itemize}
The first two conditions ensure that the stack is algebraic, the other three that it is quasi-compact with affine automorphism group (QCA).
For details on QCA stacks we refer to~\cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
Every quotient of a scheme of finite type over $k$ by an affine algebraic group is a QCA stack, and we will be mainly interested in these.

@@

\subsection{D-modules on stacks}
\label{sec:d-mod:pre:d-mods}

@@

\begin{Prop}[{\cite[\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
    \label{prop:d-mod:pre:base-change}%
    Consider a Cartesian square
    \[
        \begin{tikzcd}
            \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
            \stack X₂ \arrow[r, "g"] & \stack Y
        \end{tikzcd}
    \]
    with schematic morphism $f$ (and hence $p$).
    Then there is a base change isomorphism
    \[
        p_* q^! \isoto g^! f_*
    \]
    of functors from $\catDMod{\stack{X₁}}$ to $\catDMod{\stack{X₂}}$.
    If furthermore $f$ (and hence $p$) is proper, then this isomorphism coincides with the natural transformation
    \[
        p_* q^! →
        p_* q^! f^! f_* =
        p_* p^! g^! f_* →
        g^! f_*
    \]
    induced by $(f_*,\,f^!)$ and $(p_*,\, p^!)$ adjunctions.
\end{Prop}

\begin{Prop}
    \label{prop:d-mod:pre:projection-formula}%
    If $f\colon \stack X → \stack Y$ is a schematic morphism then the projection formula holds, i.e.~there is a functorial isomorphism
    \[
        \sheaf F \otimes f_*(\sheaf G) \cong f_*\bigl( f^! \sheaf F \otimes \sheaf G)
    \]
    for $\sheaf F ∈ \catDMod{\stack Y}$ and $\sheaf G ∈ \catDMod{\stack X}$.
\end{Prop}

\begin{Rem}
    Propositions \ref{prop:d-mod:pre:base-change} and \ref{prop:d-mod:pre:projection-formula} hold more generally when $f$ is merely a \enquote{safe} morphism.
    Alternatively they hold in full generality after replacing $f_*$ by the \enquote{renormalized de Rham pushforward}.
    We fill not use either notion in this thesis and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
\end{Rem}

@@

\begin{Prop}[{\cite[Section~2.5]{GaitsgoryRozenblyum:2014:CrystalsAndDModules}}]
    \label{prop:d-mod:recollement-std}%
    There is an exact triangle of functors
    \[
        i_*i^! → \id → j_*j^!
    \]
    on $\catDMod{\stack X}$, the adjunction morphisms
    \[
        \id → i^!i_*
        \quad\text{and}\quad
        j^!j_* → \id
    \]
    are isomorphisms, the functors $j^!i_*$ and $i^!j_*$ vanish and $i_*$ and $j_*$ are full embeddings.
\end{Prop}

On holonomic D-modules we have the additional adjoint pairs $(i^*,\, i_*)$ and $(j_!,\, j^*)$.
By applying duality to Proposition~\ref{prop:d-mod:recollement-std} we obtain the distinguished triangle
\[
    j_! j^* → \id → i_*i^*
\]
and the identity $i^*j_! = 0$ on holonomic D-modules.
Further, the functor $j_!$ is a full embedding $\catDModHol{\stack U} \hookrightarrow \catDModHol{\stack X}$.

@@

\begin{Def}
    \label{def:d-mod:pre:monodromic}%
    Let $X$ be a scheme with an action of an algebraic group $G$ and let $p\colon X → X/G$ be the quotient map.
    The \emph{monodromic} subcategory $\catDModMon{X}{G} ⊆ \catDMod{X}$ is the full subcategory generated by the essential image of $p^!\colon \catDMod{X/G} → \catDMod{X}$ (or equivalently by the essential image of $p^*$).
\end{Def}

\begin{Thm}[Contraction principle~{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
    \label{thm:d-mod:pre:contraction_principle}%
    Let $X$ be a scheme with an action by $\Gm$ that extends to an action of the monoid $\as 1$.
    Let $i\colon X^0 \hookrightarrow X$ be the closed subscheme of $\Gm$-fixed points and let $π\colon X → X^0$ be the contraction morphism induced by the $\Gm$-equivariant morphism $\as 1 → \{0\}$.
    Then there is an isomorphism of functors
    \[
        i^* \cong π_* \colon \catDModMon{X}{\Gm} → \catDMod{X^0}.
    \]
\end{Thm}

\subsection{Monads}
\label{sec:d-mod:pre:monads}

We will deduce Theorem~\ref{thm:d-mod:main} from a isomorphism of monads on $\catDMod{\stack X}$.
In this section we give a short introduction to the theory of monads and the specific constructions that we will use.
However, in the interest of readability we will mainly do so informally, skipping over the intricacies of $∞$-categories.
The interested reader can find the correct $∞$-categorical formulations in the given references.

Thus we think of a \emph{monad} on a category $\cat C$ as consisting of a triple $(T, η, μ)$, where $T\colon \cat C → \cat C$ is an endofunctor of $\cat C$, and $η\colon \id_{\cat C} → T$ and $μ\colon T∘T → T$ are natural transformations such that the diagrams
\begin{equation}
    \label{eq:d-mod:pre:monad-identities}
    \begin{tikzcd}
        T³ \arrow[r, "Tμ"] \arrow[d, "μT"'] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
    \quad\text{and}\quad
    \begin{tikzcd}
        T \arrow[r, "Tη"] \arrow[d, "ηT"'] \arrow[dr, equal] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
\end{equation}
commute.
Alternatively, we can think of $T$ being a monoid in the category of endofunctors of $\cat C$ with the monoidal structure given by composition of endofunctors.
This definition also gives the correct generalization to $∞$-categories \cite[Definition~4.7.0.1]{Lurie:2014-draft:HigherAlgebra}.

Let $X$ be an object of the category $\cat C$.
Then $T$ gives the vector space $\Hom_{\cat C}(X, TX)$ the structure of a dg algebra with multiplication map
\[
    (f,g) \mapsto μ_X ∘ Tf ∘ g,
\]
\[
    \begin{tikzcd}
        X \arrow[r, "g"] & TX \arrow[r, "Tf"] & T²X \arrow[r, "μ_X"] & TX.
    \end{tikzcd}
\]
The identities~\ref{eq:d-mod:pre:monad-identities} ensure that the algebra is associative and unital.

@@

\begin{Lem}
    \label{lem:d-mod:pre:groupoid_monad_hol}%
    Let $f\colon \stack X → \stack Y$ be a schematic morphism of stacks and let $\stack G_\cx$ be the corresponding groupoid.
    For each map $F\colon [n] → [m]$ in $\cat{Δ}^{\mathrm{op}}$ consider the corresponding square
    \[
        \begin{tikzcd}
            \stack G_{n+1} \arrow[r, "p_s"] \arrow[d, "p_{F+1}"] & \stack G_n \arrow[d, "p_F"] \\
            \stack G_{m+1} \arrow[r, "p_s"] & \stack G_m
        \end{tikzcd}
    \]
    where the vertical arrows are induced by $F$.
    Assume that for each such square the base change composition
    \[
        p_{F+1,!} p_s^! →
        p_{F+1,!} p_s^! p_F^! p_{F,!} =
        p_{F+1,!} p_{F+1}^! p_s^!  p_{F,!} →
        p_s^! p_{F,!}
    \]
    given by the adjunction morphisms is an isomorphism of functors from the category $\catDModHol{\stack G_n}$ to $\catDModHol{\stack G_{m+1}}$.
    Then the endofunctor $p_{t,!} p_s^!$ of $\catDModHol{\stack X}$ has a canonical structure of a monad and as such is isomorphic to the adjunction monad $f^!f_!$.
\end{Lem}

@@

\begin{Lem}\label{lem:d-mod:pre:hcoh}
    Let $\stack X$ be a stack.
    Then the Hochschild cohomology of $\catDMod{\stack X}$ is given by the dg algebra
    \[
        \HCoh(\catDMod{\stack X}) =
        \Hom_{\catDMod{\stack X × \stack X}}(Δ_*ω_{\stack X},\, Δ_*ω_{\stack X}).
    \]
\end{Lem}

Let $\stack X$ be any stack, where we recall that all stacks are assumed to be QCA.
We are interested in computing the Hochschild cohomology
\[
    \HCoh\bigl(\catDMod{\stack X}\bigr).
\]
Let $Δ\colon \stack X → \stack X × \stack X$ is the diagonal map, which by assumption is schematic.
The dualizing module $ω_{\stack X}$ is always holonomic.
Thus we have $\dualize Δ_* ω_{\stack X} = Δ_! k_{\stack X}$.
With this we observe that
\begin{align*}
    \HCoh\bigl(\catDMod{\stack X}\bigr)
    & = \Hom_{\catDMod{\stack X × \stack X}}(Δ_* ω_{\stack X},\, Δ_* ω_{\stack X}) & &\text{(Lemma~\ref{lem:d-mod:pre:hcoh})} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(Δ_! k_{\stack X},\, Δ_! k_{\stack X})} & & \text{(duality)} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})} & & \text{(adjunction)} \\
    & = \opalg{\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr)},
\end{align*}
where the algebra structure on $\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr) = \Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})$ is the one induced by the $(Δ_!,Δ^!)$-adjunction monad.
Consider the Cartesian square
\[
    \begin{tikzcd}
        \ls{\stack X} \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
Let us assume for the moment that $Δ$ (and hence $p_i$) was proper.
Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:d-mod:pre:monads} we have an isomorphism of monads
\begin{equation}
    \label{eq:d-mod:central_iso}
    p_{2,!} p₁^! → Δ^!Δ_!,
\end{equation}
which induces an isomorphism of algebras
\[
    \ΓdR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)
    →
    \ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr).
\]
Of course, if $X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
Thus in general \eqref{eq:d-mod:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{2,!} p₁^!$.
We would like to apply Lemma~\ref{lem:d-mod:pre:groupoid_monad_hol} to construct a monad in special cases.
Thus the goal of this chapter is to give a criterion for the assumptions of Lemma~\ref{lem:d-mod:pre:groupoid_monad_hol}, i.e.~for base change to hold.

\begin{Ex}
    The base change morphism \eqref{eq:d-mod:central_iso} is also an isomorphism if $Δ$ is smooth.
    In particular this implies that the \enquote{naive expectation} holds for $\stack X = \B G$ for any algebraic group $G$, i.e.~we have
    \[
        \HCoh(\catDMod{\B G}) = \opalg{\ΓdR\bigl(\B G,\, p_{2,!} p₁^! k_{\B G}\bigr)}.
    \]
    An argument similar to \cite{BenZvi:mathoverflow:CohomologyOfGmodG} shows that there is a further isomorphism
    \[
        \ΓdR\bigl(\B G,\, p_{2,!} p₁^! k_{\stack X}\bigr) \cong
        \ΓdR(G, k_G)^\dual \otimes \ΓdR(\B G, k_{\B G}).
    \]
    Alternatively, we can use the identification
    \[
        \catDMod{\B G} \cong \catModules{\ΓdR(G, k_{G})^\dual},
    \]
    where the algebra structure on $\ΓdR(G, k_G)^\dual$ is induced by the group multiplication \cite[Section~7.2]{DrinfeldGaitsgory:2013:FinitenessQuestions}.
    If $G$ is reductive, then $\ΓdR(G, k_G)^\dual$ is an exterior algebra and thus its Hochschild cohomology can be computed directly.
\end{Ex}

\section{Base change}
\subsection{A lemma on base change}\label{sec:d-mod:strategy:base-change}

>>>>

A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
We will review the general setup and basic properties of D-modules on (QCA) stacks in Section~\ref{sec:pre}.
The upshot is that we have an isomorphism of dg algebras
\begin{equation}
    \label{eq:intro:d-mod-hcoh}
    \HCoh(\catDMod{\stack X}) \cong \Hom_{\catDMod{X×X}}(Δ_*ω_{\stack X}, Δ_*ω_{\stack X}),
\end{equation}
where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Lemma show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de Rham cohomology of $\stack X$.
However, if $\stack X$ is not an algebraic space (and hence $Δ$ is not proper) then the situation becomes more complicated.

By Verdier duality and adjunction we can always rewrite \eqref{eq:intro:d-mod-hcoh} as
\[
    \HCoh(\catDMod{\stack X}) \cong
    \opalg{\Hom_{\catDMod{X}}(k_{\stack X}, Δ^!Δ_!k_{\stack X})} =
    \opalg{\ΓdR(\stack X, Δ^!Δ_!k_{\stack X})}.
\]
It is now tempting to look at the Cartesian square
\[
    \begin{tikzcd}
        \ls \stack X \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
where
\[
    \ls \stack X = \stack X ×\limits_{\stack X × \stack X} \stack X
\]
is the (derived) loop space of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
Naively we could expect the existence of an isomorphism
\begin{equation}
    \label{eq:intro:naive}
    \ΓdR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
    \ΓdR(\stack X, p_{2,!}p₁^! k_{\stack X}).
\end{equation}
Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\as1$ is an easy counter-example).

In Section~\ref{sec:base-change} we will investigate how to quantify the cone of the morphism
\[
    p_{2,!}p₁^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
\]
and thus the failure of the naive isomorphism \eqref{eq:intro:naive} to hold.
As an application, we will prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.

\begin{Thm}\label{thm:main}
    Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
    Then there is a canonical isomorphism of algebras
    \[
        \HCoh\bigl(\catDMod{X/G}\bigr)
        \cong
        \opalg{\ΓdR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)},
    \]
    where the algebra structure on $\ΓdR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
\end{Thm}

\section{Prerequisites}%
\label{sec:pre}

We fix an algebraically closed base field $k$ of characteristic $0$.
All stacks in this thesis are assumed to be algebraic QCA stacks over $k$.
As we will summarize in Section~\ref{sec:pre:d-mods}, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
In particular for any stack $\stack X$ we have:
\begin{itemize}
    \item The diagonal morphism $Δ\colon \stack X → \stack X × \stack X$ is schematic.
    \item There exists a scheme $Z$ with a smooth and surjective map $Z → \stack X$.
    \item $\stack X$ is quasi-compact.
    \item The automorphism groups of the geometric points of $\stack X$ are affine.
    \item The loop space (or inertia stack) $\ls \stack X = \stack X ×_{\stack X × \stack X} \stack X$ is of finite presentation over $\stack X$.
\end{itemize}
The first two conditions ensure that the stack is algebraic, the other three that it is quasi-compact with affine automorphism group (QCA).
For details on QCA stacks we refer to~\cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
Every quotient of a scheme of finite type over $k$ by an affine algebraic group is a QCA stack, and we will be mainly interested in these.

@@

\subsection{D-modules on stacks}
\label{sec:pre:d-mods}

@@

\begin{Prop}[{\cite[\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
    \label{prop:pre:base-change}%
    Consider a Cartesian square
    \[
        \begin{tikzcd}
            \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
            \stack X₂ \arrow[r, "g"] & \stack Y
        \end{tikzcd}
    \]
    with schematic morphism $f$ (and hence $p$).
    Then there is a base change isomorphism
    \[
        p_* q^! \isoto g^! f_*
    \]
    of functors from $\catDMod{\stack{X₁}}$ to $\catDMod{\stack{X₂}}$.
    If furthermore $f$ (and hence $p$) is proper, then this isomorphism coincides with the natural transformation
    \[
        p_* q^! →
        p_* q^! f^! f_* =
        p_* p^! g^! f_* →
        g^! f_*
    \]
    induced by $(f_*,\,f^!)$ and $(p_*,\, p^!)$ adjunctions.
\end{Prop}

\begin{Prop}
    \label{prop:pre:projection-formula}%
    If $f\colon \stack X → \stack Y$ is a schematic morphism then the projection formula holds, i.e.~there is a functorial isomorphism
    \[
        \sheaf F \otimes f_*(\sheaf G) \cong f_*\bigl( f^! \sheaf F \otimes \sheaf G)
    \]
    for $\sheaf F ∈ \catDMod{\stack Y}$ and $\sheaf G ∈ \catDMod{\stack X}$.
\end{Prop}

\begin{Rem}
    Propositions \ref{prop:pre:base-change} and \ref{prop:pre:projection-formula} hold more generally when $f$ is merely a \enquote{safe} morphism.
    Alternatively they hold in full generality after replacing $f_*$ by the \enquote{renormalized de Rham pushforward}.
    We fill not use either notion in this thesis and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
\end{Rem}

@@

\begin{Prop}[{\cite[Section~2.5]{GaitsgoryRozenblyum:2014:CrystalsAndDModules}}]
    \label{prop:recollement-std}%
    There is an exact triangle of functors
    \[
        i_*i^! → \id → j_*j^!
    \]
    on $\catDMod{\stack X}$, the adjunction morphisms
    \[
        \id → i^!i_*
        \quad\text{and}\quad
        j^!j_* → \id
    \]
    are isomorphisms, the functors $j^!i_*$ and $i^!j_*$ vanish and $i_*$ and $j_*$ are full embeddings.
\end{Prop}

On holonomic D-modules we have the additional adjoint pairs $(i^*,\, i_*)$ and $(j_!,\, j^*)$.
By applying duality to Proposition~\ref{prop:recollement-std} we obtain the distinguished triangle
\[
    j_! j^* → \id → i_*i^*
\]
and the identity $i^*j_! = 0$ on holonomic D-modules.
Further, the functor $j_!$ is a full embedding $\catDModHol{\stack U} \hookrightarrow \catDModHol{\stack X}$.

@@

\begin{Def}
    \label{def:pre:monodromic}%
    Let $X$ be a scheme with an action of an algebraic group $G$ and let $p\colon X → X/G$ be the quotient map.
    The \emph{monodromic} subcategory $\catDModMon{X}{G} ⊆ \catDMod{X}$ is the full subcategory generated by the essential image of $p^!\colon \catDMod{X/G} → \catDMod{X}$ (or equivalently by the essential image of $p^*$).
\end{Def}

\begin{Thm}[Contraction principle~{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
    \label{thm:pre:contraction_principle}%
    Let $X$ be a scheme with an action by $\Gm$ that extends to an action of the monoid $\as 1$.
    Let $i\colon X^0 \hookrightarrow X$ be the closed subscheme of $\Gm$-fixed points and let $π\colon X → X^0$ be the contraction morphism induced by the $\Gm$-equivariant morphism $\as 1 → \{0\}$.
    Then there is an isomorphism of functors
    \[
        i^* \cong π_* \colon \catDModMon{X}{\Gm} → \catDMod{X^0}.
    \]
\end{Thm}

\subsection{Monads}
\label{sec:pre:monads}

We will deduce Theorem~\ref{thm:main} from a isomorphism of monads on $\catDMod{\stack X}$.
In this section we give a short introduction to the theory of monads and the specific constructions that we will use.
However, in the interest of readability we will mainly do so informally, skipping over the intricacies of $∞$-categories.
The interested reader can find the correct $∞$-categorical formulations in the given references.

Thus we think of a \emph{monad} on a category $\cat C$ as consisting of a triple $(T, η, μ)$, where $T\colon \cat C → \cat C$ is an endofunctor of $\cat C$, and $η\colon \id_{\cat C} → T$ and $μ\colon T∘T → T$ are natural transformations such that the diagrams
\begin{equation}
    \label{eq:pre:monad-identities}
    \begin{tikzcd}
        T³ \arrow[r, "Tμ"] \arrow[d, "μT"'] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
    \quad\text{and}\quad
    \begin{tikzcd}
        T \arrow[r, "Tη"] \arrow[d, "ηT"'] \arrow[dr, equal] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
\end{equation}
commute.
Alternatively, we can think of $T$ being a monoid in the category of endofunctors of $\cat C$ with the monoidal structure given by composition of endofunctors.
This definition also gives the correct generalization to $∞$-categories \cite[Definition~4.7.0.1]{Lurie:2014-draft:HigherAlgebra}.

Let $X$ be an object of the category $\cat C$.
Then $T$ gives the vector space $\Hom_{\cat C}(X, TX)$ the structure of a dg algebra with multiplication map
\[
    (f,g) \mapsto μ_X ∘ Tf ∘ g,
\]
\[
    \begin{tikzcd}
        X \arrow[r, "g"] & TX \arrow[r, "Tf"] & T²X \arrow[r, "μ_X"] & TX.
    \end{tikzcd}
\]
The identities~\ref{eq:pre:monad-identities} ensure that the algebra is associative and unital.

@@

\begin{Lem}
    \label{lem:pre:groupoid_monad_hol}%
    Let $f\colon \stack X → \stack Y$ be a schematic morphism of stacks and let $\stack G_\cx$ be the corresponding groupoid.
    For each map $F\colon [n] → [m]$ in $\cat{Δ}^{\mathrm{op}}$ consider the corresponding square
    \[
        \begin{tikzcd}
            \stack G_{n+1} \arrow[r, "p_s"] \arrow[d, "p_{F+1}"] & \stack G_n \arrow[d, "p_F"] \\
            \stack G_{m+1} \arrow[r, "p_s"] & \stack G_m
        \end{tikzcd}
    \]
    where the vertical arrows are induced by $F$.
    Assume that for each such square the base change composition
    \[
        p_{F+1,!} p_s^! →
        p_{F+1,!} p_s^! p_F^! p_{F,!} =
        p_{F+1,!} p_{F+1}^! p_s^!  p_{F,!} →
        p_s^! p_{F,!}
    \]
    given by the adjunction morphisms is an isomorphism of functors from the category $\catDModHol{\stack G_n}$ to $\catDModHol{\stack G_{m+1}}$.
    Then the endofunctor $p_{t,!} p_s^!$ of $\catDModHol{\stack X}$ has a canonical structure of a monad and as such is isomorphic to the adjunction monad $f^!f_!$.
\end{Lem}

@@

\begin{Lem}\label{lem:pre:hcoh}
    Let $\stack X$ be a stack.
    Then the Hochschild cohomology of $\catDMod{\stack X}$ is given by the dg algebra
    \[
        \HCoh(\catDMod{\stack X}) =
        \Hom_{\catDMod{\stack X × \stack X}}(Δ_*ω_{\stack X},\, Δ_*ω_{\stack X}).
    \]
\end{Lem}

Let $\stack X$ be any stack, where we recall that all stacks are assumed to be QCA.
We are interested in computing the Hochschild cohomology
\[
    \HCoh\bigl(\catDMod{\stack X}\bigr).
\]
Let $Δ\colon \stack X → \stack X × \stack X$ is the diagonal map, which by assumption is schematic.
The dualizing module $ω_{\stack X}$ is always holonomic.
Thus we have $\dualize Δ_* ω_{\stack X} = Δ_! k_{\stack X}$.
With this we observe that
\begin{align*}
    \HCoh\bigl(\catDMod{\stack X}\bigr)
    & = \Hom_{\catDMod{\stack X × \stack X}}(Δ_* ω_{\stack X},\, Δ_* ω_{\stack X}) & &\text{(Lemma~\ref{lem:pre:hcoh})} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(Δ_! k_{\stack X},\, Δ_! k_{\stack X})} & & \text{(duality)} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})} & & \text{(adjunction)} \\
    & = \opalg{\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr)},
\end{align*}
where the algebra structure on $\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr) = \Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})$ is the one induced by the $(Δ_!,Δ^!)$-adjunction monad.
Consider the Cartesian square
\[
    \begin{tikzcd}
        \ls{\stack X} \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
Let us assume for the moment that $Δ$ (and hence $p_i$) was proper.
Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:pre:monads} we have an isomorphism of monads
\begin{equation}
    \label{eq:central_iso}
    p_{2,!} p₁^! → Δ^!Δ_!,
\end{equation}
which induces an isomorphism of algebras
\[
    \ΓdR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)
    →
    \ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr).
\]
Of course, if $X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
Thus in general \eqref{eq:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{2,!} p₁^!$.
We would like to apply Lemma~\ref{lem:pre:groupoid_monad_hol} to construct a monad in special cases.
Thus the goal of this chapter is to give a criterion for the assumptions of Lemma~\ref{lem:pre:groupoid_monad_hol}, i.e.~for base change to hold.

\begin{Ex}
    The base change morphism \eqref{eq:central_iso} is also an isomorphism if $Δ$ is smooth.
    In particular this implies that the \enquote{naive expectation} holds for $\stack X = \B G$ for any algebraic group $G$, i.e.~we have
    \[
        \HCoh(\catDMod{\B G}) = \opalg{\ΓdR\bigl(\B G,\, p_{2,!} p₁^! k_{\B G}\bigr)}.
    \]
    An argument similar to \cite{BenZvi:mathoverflow:CohomologyOfGmodG} shows that there is a further isomorphism
    \[
        \ΓdR\bigl(\B G,\, p_{2,!} p₁^! k_{\stack X}\bigr) \cong
        \ΓdR(G, k_G)^\dual \otimes \ΓdR(\B G, k_{\B G}).
    \]
    Alternatively, we can use the identification
    \[
        \catDMod{\B G} \cong \catModules{\ΓdR(G, k_{G})^\dual},
    \]
    where the algebra structure on $\ΓdR(G, k_G)^\dual$ is induced by the group multiplication \cite[Section~7.2]{DrinfeldGaitsgory:2013:FinitenessQuestions}.
    If $G$ is reductive, then $\ΓdR(G, k_G)^\dual$ is an exterior algebra and thus its Hochschild cohomology can be computed directly.
\end{Ex}

\section{Base change}
\label{sec:base-change}
\subsection{A lemma on base change}\label{sec:base-change:base-change}

Consider a Cartesian diagram of stacks
\[
    \begin{tikzcd}
        \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
        \stack X₂ \arrow[r, "g"] & \stack Y
    \end{tikzcd}
\]
with $f$ and $g$ schematic.
We have a morphism of functors $\catDModHol{\stack X₁} → \catDModHol{\stack X₂}$,
\begin{equation}
    \label{eq:base-change-morphism}
     p_! q^! → g^! f_!
\end{equation}
induced by adjunctions
\begin{equation}
    \label{eq:base-change-adjunctions}
    p_! q^! →
    p_! q^! f^! f_! =
    p_! p^! g^! f_! →
    g^! f_!.
\end{equation}
If $f$ is proper, then \eqref{eq:base-change-morphism} is an isomorphism by Proposition~\ref{prop:pre:base-change}.
To understand the behavior for non-proper $f$, we will approximate it by a proper morphism.
